### 2023-01-30 ART_Dodig-Crnkovic/Dodig-Crnkovic.tex
Toscano article added

\begin{artengenv}{Gordana Dodig-Crnkovic}
	{In search of a~common, information-processing, agency-based framework for anthropogenic, biogenic, and abiotic cognition and intelligence}
	{In search of a~common, information-processing, agency-based\ldots}
	{In search of a~common, information-processing, agency-based framework for anthropogenic, biogenic, and abiotic cognition and intelligence}
	{Chalmers University of Technology, University of Gothenburg and Mälardalen University, Sweden}
	{Learning from contemporary natural, formal, and social sciences, especially from current biology, as well as from humanities, particularly contemporary philosophy of nature, requires updates of our old definitions of cognition and intelligence. The result of current insights into basal cognition of single cells and evolution of multicellular cognitive systems within the framework of extended evolutionary synthesis (EES) helps us better to understand mechanisms of cognition and intelligence as they appear in nature. New understanding of information and processes of physical (morphological) computation contribute to novel possibilities that can be used to inspire the development of abiotic cognitive systems (cognitive robotics), cognitive computing and artificial intelligence.
	}
	{information, computation, cognition, intelligence, extended evolutionary synthesis, anthropogenic, biogenic and abiotic cognition}

>>>>

\begin{artengenv}{Gordana Dodig-Crnkovic}
	{In search of a~common, information-processing, agency-based framework for anthropogenic, biogenic, and abiotic cognition and intelligence}
	{In search of a~common, information-processing, agency-based\ldots}
	{In search of a~common, information-processing, agency-based\\framework for anthropogenic, biogenic, and abiotic cognition\\and intelligence}
	{Chalmers University of Technology,\\University of Gothenburg\\and Mälardalen University, Sweden}
	{Learning from contemporary natural, formal, and social sciences, especially from current biology, as well as from humanities, particularly contemporary philosophy of nature, requires updates of our old definitions of cognition and intelligence. The result of current insights into basal cognition of single cells and evolution of multicellular cognitive systems within the framework of extended evolutionary synthesis (EES) helps us better to understand mechanisms of cognition and intelligence as they appear in nature. New understanding of information and processes of physical (morphological) computation contribute to novel possibilities that can be used to inspire the development of abiotic cognitive systems (cognitive robotics), cognitive computing and artificial intelligence.
	}
	{information, computation, cognition, intelligence, extended evolutionary synthesis, anthropogenic, biogenic and abiotic cognition.}
